\documentclass[10pt,a4paper]{article}

% Encoding and fonts
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Math and symbols
\usepackage{amsmath, amssymb, amsfonts}

% Graphics and figures
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

% Better referencing
\usepackage{hyperref}
\usepackage{cleveref}

% Bibliography
\usepackage[numbers]{natbib}

% Formatting
\usepackage{setspace}
\onehalfspacing
\usepackage{geometry}
\geometry{margin=2.5cm}

% Title info
\title{Semester Project Report \\ \large Neural Networks (AI)}
\author{
  Team Members: Alice Example, Bob Example, Carol Example \\
  University of Groningen
}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
\noindent
A concise ($\approx$10 lines) summary of the task, dataset, methods, and main results.
\end{abstract}

\tableofcontents
\newpage

\section{Introduction}
State your project task (given or self-chosen).  
Briefly describe dataset(s) and objectives.  
Keep it short, direct, and specific to your project.

\section{Data}
\begin{itemize}
  \item Source of dataset
  \item Size and type (tabular, images, time series…)
  \item Key characteristics (with plots or descriptive stats)
  \item Any preprocessing or cleaning
\end{itemize}

\section{Methods and Experiments}
\subsection{Pipeline Overview}
Diagram or list of your full pipeline: preprocessing, model, optimization.  

\subsection{Model Description}
- Architecture (MLP, CNN, etc.), with math or pseudocode if needed.  
- Loss function, optimizer, regularization.  

\subsection{Training Procedure}
- Cross-validation setup, train/test split.  
- Hyperparameters and how you chose them.  

\section{Results}
\begin{itemize}
  \item Performance metrics (accuracy, MSE, etc.)
  \item Learning curves or confusion matrices
  \item Compare with baseline(s)
\end{itemize}

\section{Discussion}
\begin{itemize}
  \item What worked well and why
  \item What didn't work, limitations
  \item Possible improvements or future work
\end{itemize}

\section{Conclusion}
Wrap up: summarize objectives, approach, key findings, and lessons learned.

\section*{References}
\bibliographystyle{plainnat}
\bibliography{references}

\appendix
\section{Use of AI Tools}
Briefly document how (if at all) ChatGPT or other LLMs were used in writing or coding.

\section{Additional Figures / Materials}
Include extra plots, tables, or examples here if needed.

\end{document}
